\chapter{Ultrafast Optics}
% \lecture{2}{9 Aug. 08:00}{Telescope Array}

\section{Ultra-Short Pulses}

\begin{table}[h!]
    \centering
    \caption{The colors of the visible light spectrum}
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Color} & \textbf{Wavelength interval} & \textbf{Cycle time interval} \\
        \hline
        \textcolor{red}{Red} & $\sim$700--635 nm & $\sim$2.3--2.1 fs \\
        \hline
        \textcolor{orange}{Orange} & $\sim$635--590 nm & $\sim$2.1--2.0 fs \\
        \hline
        \textcolor{yellow}{Yellow} & $\sim$590--560 nm & $\sim$2.0--1.9 fs \\
        \hline
        \textcolor{green}{Green} & $\sim$560--520 nm & $\sim$1.9--1.7 fs \\
        \hline
        \textcolor{cyan}{Cyan} & $\sim$520--490 nm & $\sim$1.7--1.6 fs \\
        \hline
        \textcolor{blue}{Blue} & $\sim$490--450 nm & $\sim$1.6--1.5 fs \\
        \hline
        \textcolor{violet}{Violet} & $\sim$450--400 nm & $\sim$1.5--1.3 fs \\
        \hline
    \end{tabular}
\end{table}

The swiftest chemical reaction known (radiolysis of water) is about 46 fs, while the average chemical reaction is about 200 fs. A ray of light travels about 0.3 $\mu$m in one femtosecond, approzimately the diameter of a virus.

\section{Laser}
Laser is the acronym for \textbf{Light Amplification by Stimulated Emission of Radiation}.

\subsection{Poisson Distribution}
Photons from a stable laser source can be appropriately described by a Poisson distribution, since the number of photons arriving at an ideal detector in a given time interval is a random variable. The Poisson distribution is defined as:

\begin{equation}
    \operatorname{Pois}(n; \lambda) = \frac{\lambda^n e^{-\lambda}}{n!}
\end{equation}

where \( n \) is the number of photons detected and \( \lambda \) is the average number of photons arriving in the time interval.



\section{Noise in Optical Systems}
Noise can be quantified using various metrics, including the signal-to-noise ratio (SNR), which compares the level of the desired signal to the level of background noise. In optical systems, noise can arise from various sources, including thermal fluctuations, shot noise, and electronic noise. 

Main classes of noise in the literature include: shot noise, quantum noise, thermal noise, flicker noise, and phase-sensitive/insensitive noise.

\section{Optical Parametric Amplifier}
An OPA process is responsible for the amplification of ultrafast laser pulses.

\section{Structure of NOPA}
